New Biomass Pools Workflow

### 2023-06-14 NewBiomassPoolsWorkflow.Rmd
outputs of load_nc work for N

```
So we want "N" nitrogen output. In theory this can be achieved with `atlantisom::load_nc`with `select_variable = "N"`.

@@

testNpools <- load_nc(dir = dir,
                  file_nc = nc_out,
                  bps = bps,
                  fgs = fgs,
                  select_groups = select_groups,
                  select_variable = "N",
                  check_acronyms = TRUE,
                  bboxes = boxes)
```

I don't think we have a function that converts N to biomass but there are pieces in other functions.

>>>>

```
So we want "N" nitrogen output. In theory this can be achieved with `atlantisom::load_nc`with `select_variable = "N"`. Looks like it works, output is N for our selected biomass pool species over all polygons, layers, and times.

@@

testNpools <- load_nc(dir = dir,
                  file_nc = nc_out,
                  bps = bps,
                  fgs = fgs,
                  select_groups = select_groups,
                  select_variable = "N",
                  check_acronyms = TRUE,
                  bboxes = boxes)

unique(testNpools$species)
```

I don't think we have a function that aggregates over layets and converts N to biomass but there are pieces in other functions.
